Estimating Correspondences of Deformable Objects ``In-The-Wild"

### 2015-11-03 contents/introduction.tex
Updates from ShareLaTeX

% \clearpage
\begin{figure}[t!]
    \centering
    \begin{subfigure}[b]{0.145\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_0_0}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.145\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_0_1}
    \end{subfigure}
   	\hfill
    \begin{subfigure}[b]{0.145\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_0_2}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.075\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_0}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.075\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_1}
    \end{subfigure}
   	\hfill
    \begin{subfigure}[b]{0.075\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.07\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.07\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_4}
    \end{subfigure}
   	\hfill
    \begin{subfigure}[b]{0.07\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_5}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.06\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_0}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.06\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_1}
    \end{subfigure}
   	\hfill
    \begin{subfigure}[b]{0.06\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.06\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.06\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_4}
    \end{subfigure}
   	\hfill
    \begin{subfigure}[b]{0.06\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_5}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.075\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_3_0}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.075\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_3_1}
    \end{subfigure}
   	\hfill
    \begin{subfigure}[b]{0.075\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_3_2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.075\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_3_3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.075\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_3_4}
    \end{subfigure}
   	\hfill
    \begin{subfigure}[b]{0.075\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_3_5}
    \end{subfigure}
    \caption{Demonstration of classical landmark annotation and curve annotation of faces, ears, bottles and human actions.}
    \label{fig:intro}
\end{figure}

>>>>

% \clearpage

\begin{figure}[t!]
    \centering
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/BBCPose/bad_anno-1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/BBCPose/bad_anno-2}
    \end{subfigure}
  	\hfill
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/BBCPose/bad_anno-3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/BBCPose/bad_anno-4}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FashionPose/bad_anno-1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FashionPose/bad_anno-2}
    \end{subfigure}
  	\hfill
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FashionPose/bad_anno-3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FashionPose/bad_anno-4}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FLIC/bad_anno-1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FLIC/bad_anno-2}
    \end{subfigure}
  	\hfill
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FLIC/bad_anno-3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FLIC/bad_anno-4}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/MPII/bad_anno-1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/MPII/bad_anno-2}
    \end{subfigure}
  	\hfill
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/MPII/bad_anno-3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/MPII/bad_anno-4}
    \end{subfigure}

    \caption{Demonstration of classical landmark annotation and curve annotation of faces, ears, bottles and human actions.}
    \label{fig:intro}
\end{figure}
